The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-03-24 repeater-vladata.tex
better rate discussion

\subsection{Rate Comparison}

The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. \citet{2013Sci...341...53T} used this approach to estimate a rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming an isotropic emitter in a Milky Way-type galaxy out to a characteristic redshift horizon of 0.9. This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as GRBs or rarer SNe.

However, inferences based on this and related rates are difficult, since they are strongly dependent on the sensitivity of the telescopes. Here we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class. We also update the volumetric rate to use the latest projected FRB rate \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.

We recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects. The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$.

The characteristic distance scale for FRBs can be inferred from the detectability of \frb. The projected FRB rate is defined for a fluence limit of 1 Jy ms which is detectable out to $z=2\ for the Parkes surveys that have detected the most FRBs. This distance is consistent with that inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C}. This assumes that DM is dominated by the IGM \citep[$DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$\ for realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}, although other contributions are likely significant \citep{2014ApJ...780L..33M}. An independent argument for a characteristic distance of $z=2$\ is that it corresponds to the peak the in the cosmic star formation history \citep{2014ARA&A..52..415M} and most leading models for FRBs are driven by star formation \citep{2016MNRAS.462..941L,2016ApJ...826..226K,2017arXiv170104815K}.

Using an assumed horizon redshift of 2, we estimate a rate of $R_p = 10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$. Narrow burst spectral structure implies that observations underestimate by missing bursts that fall outside the observing band. For a typical burst envelope width of 500~MHz centered at GHz-scale frequencies, past observations (typically using bandwidths of a few hundred MHz near 1.4~GHz) would underestimate the rate by a factor of a few. There is also relatively little constraint on the beaming factor \citep[$\sim0.1$ for pulsars;][]{1998MNRAS.298..625T}. This estimate also assumes that propagation effects do not significantly affect the detectability of FRBs, although scintillation likely plays a significant role \citep{2015MNRAS.451.3278M, CORDES}.

This revised volumetric estimate makes many assumptions, but is now appropriate for comparison to rates used for other classes of transient. The LGRB and SLSN-I rates are {\color{red}xx} and $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{?,2012Sci...337..927G}. These higher-energy transients can be considered sources of FRB-generating systems if all FRBs repeat with $N_r\approx10^3$\ with burst energies near $10^{40}$\ erg. \citep{2017arXiv170102370M} calculate the maximum number of bursts that can be powered the magnetic field of a magnetar as $\approx300$, assmuming $\Omega_b=0.1$\ and $E_b=10^{40}$\ erg. This is in rough agreement, given the assumptions required in both both the observations and modeling.

@@

%\begin{figure}[htb]
%\begin{center}
%\includegraphics[width=0.9\columnwidth]{}
%\caption{
%\label{fig:name}}
%\end{center}
%\end{figure}

%\begin{table}
%\caption{Caption}
%\footnotesize
%\centering
%\begin{tabular}{l|cc|cc|c}
%\hline
%Field       & RA          & Dec   & Lon. & Lat.     & Time \\
%            & \multicolumn{2}{|c|}{(J2000)}  & \multicolumn{2}{|c|}{(Galactic; deg)} & (hrs) \\ \hline
%RA02        & 2:27:53  &  +9:13:24 & 159.0 & --46.8    & 26.25 \\
%PSR J2248-0101 & 22:48:27 & --1:1:48 & 69.3 & --50.6 & 6.5 \\ \hline
%\end{tabular}
%\label{fields}
%\end{table}

>>>>

\subsection{Revised Volumetric Rate}

%The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. 
\citet{2013Sci...341...53T} estimated an isotropic FRB rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by calculating the number of Milky Way-type galaxies out to a distance implied by assming all extragalactic DM originates in the IGM \citep[$z\approx0.9$\ for $DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}. This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as LGRBs or rarer SNe \citep{2006ARA&A..44..507W}. However, this estimate depends on the telescope sensitivity, so is not easy to compare to other estimates based on source counts. Here we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class.

First, we recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects. The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$. The newest estimates of the projected FRB rate are lower by a factor of 5 \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.

The burst rate depends on the fluence limit of past FRB surveys, but \frb\ has an absolute energy scale that can be used to estimate FRB fluence at a given distance. At the typical Parkes survey parameters \citep{}, a fluence limit of 1~Jy~ms is detectable at $z\approx1$. The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but it is likely that DM has significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}. For reference, we note that cosmic star formation rate peaks between redshift of 2 and 3\citep{2014ARA&A..52..415M}.

Using an assumed horizon redshift of 1, we estimate a rate of $R_p \approx 5\times10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$. The narrow burst spectral structure seen for \frb\ implies that observations have undercounted the rate by a factor of a few by ignoring bursts outside the band. There is also relatively little constraint on the beaming factor \citep[$\sim0.1$ for pulsars;][]{1998MNRAS.298..625T}. This estimate also assumes that propagation effects do not significantly affect the detectability of FRBs, although scintillation likely plays a significant role \citep{2015MNRAS.451.3278M, CORDES}.

Despite its many assumptions, this is the first volumetric rate appropriate for comparison to rates used for other classes of transient. The LGRB and SLSN-I rates are {\color{red}xx} and $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{?,2012Sci...337..927G}. Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat with $xx$\ and $5\times10^3$, respectively (assuming burst energies of $10^{40}$\ erg). \citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered its magnetic field as $\approx300$. Under the magnetar mdoel for FRBs, LGRBs, and SLSN-I, this rate comparison suggests that the LGRB rate is most consistent with the FRB rate.

@@
